Accessible and Usable Datasets yet Majority are Bronze-Graded and not Updated Regularly

### 2025-05-14 paper/paper.qmd
Updated abstract in qmd

---
title: "Accessible and Usable Datasets yet Majority are Bronze-Graded and not Updated Regularly"
subtitle: "An analysis of the data quality of datasets available on the Open Data Toronto Portal (As of May 13, 2025)"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/data-quality](https://github.com/moonsdust/data-quality)."
date: today
date-format: long
abstract: "As one of the central hubs for data on the City of Toronto that are used in the media and in policy-making, we conducted analysis on the quality of Open Data Toronto's data catalogue. We found that despite Open Data Toronto's extensive dataset catalogue being accessible and usable, 56% of their datasets are graded bronze and bronze-graded datasets are less likely to be updated the more completed they are. However we also found that metadata fields were less likely to be filled for gold-graded and silver-graded datasets. These findings can help reporters, policy-makers, and anyone interested in using datasets from Open Data Toronto's catalogue make an inform decision of what datasets to choose."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
execute:
  python: ".venv/bin/python"
  external: true
---
```{python}
#| include: false
#| warning: false
#| message: false

>>>>

---
title: "Accessible and Usable Datasets yet Majority are Bronze-Graded and not Updated Regularly"
subtitle: "An analysis of the data quality of datasets available on the Open Data Toronto Portal (As of May 13, 2025)"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/data-quality](https://github.com/moonsdust/data-quality)."
date: today
date-format: long
abstract: "As one of the central hubs for Toronto-related data, we conducted analysis on the data quality of Open Data Toronto's catalogue. We found that despite Open Data Toronto's extensive dataset catalogue being accessible and usable, 56% of their datasets are graded bronze and bronze-graded datasets are less likely to be updated the more complete they are. However, we also found that metadata fields were less likely to be filled for gold-graded and silver-graded datasets. These findings can help reporters, policy-makers, and anyone interested in using datasets from Open Data Toronto's catalogue make an inform decision of what datasets to choose for purposes like journalism and in policy-making."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
execute:
  python: ".venv/bin/python"
  external: true
---
```{python}
#| include: false
#| warning: false
#| message: false
